15th International Satisfiability Modulo Theories Competition (SMT-COMP 2021): Rules and Procedures

### 2021-05-01 rules/rules21.tex
Updated dates

\title{15th International Satisfiability Modulo Theories Competition
  (SMT-COMP 2020): Rules and Procedures}

@@

\begin{description}
\item[March~1] Deadline for new benchmark contributions.
\item[April~20] Final versions of competition tools (e.g., benchmark
  scrambler) are made available.  Benchmark libraries are frozen.
\item[May~4] Deadline for first versions of solvers (for all tracks),
  including information about which tracks and divisions are being
  entered, and magic numbers for benchmark scrambling.
\item[May~26] Deadline for final versions of solvers, including
  system descriptions.
\item[May~27] Opening value of NYSE Composite Index used to compute
  random seed for competition tools.
\item[July~5/6] SMT Workshop; end of competition, presentation of
  results.
\end{description}

@@

SMT-COMP~2020 is part of the SMT Workshop~2020
(\url{http://smt-workshop.cs.uiowa.edu/2020/index.shtml}),
which is affiliated with IJCAR~2020 (\url{https://ijcar2020.org/}).
The SMT Workshop will include a block of time to present the results of the
competition.
%
Accordingly, researchers are highly encouraged to submit both new
benchmarks and new or improved solvers to raise the level of
competition and advance the state-of-the-art in automated SMT problem
solving.

SMT-COMP 2020 will have four tracks: the \maintrack (before 2019: Main Track),
the \inctrack (before 2019: Application Track), the \ucoretrack, and the
\mvaltrack.
%
Within each track there are multiple divisions, where each division
uses benchmarks from a specific SMT-LIB logic (or group of logics).
We will recognize winners as measured by number of benchmarks solved
(taking into account the weighting detailed in
Section~\ref{sec:scoring}); we will also recognize solvers based on
additional criteria.

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Liana Hadarean,
  Matthias Heizmann, Aina Niemetz, Albert Oliveras, Giles Reger, Aaron Stump,
  and Tjark Weber.}  describes the rules and competition procedures for
SMT-COMP~2020.
%
As in previous years, we have revised the rules slightly.  Some rule
changes in 2020 aim specifically at making the competition more
manageable to run, as both the popularity of the competition and the
benchmark library have grown over time.
%
The principal changes from the previous competition rules are the following:
\begin{itemize}
  \item {\bf The option \akey{:print-success} is explicitly set to
    true or false.}  Previous competitions set this option to
    \akey{true} for the incremental track.  In addition, this
    competition will set the option to \akey{false} for all other
    tracks.
    \rationale{According to the standard the default value of
      \akey{:print-success} is true.  So a conforming solver would
      unnecessarily print \akey{success} after each command that needs
      to be stored and skipped by the post-processors.  Additionally,
      solvers can use this option as indication whether incremental
      checking is desired.}

@@

SMT-COMP entrants must be submitted via StarExec (solvers) \emph{and}
the above web form (accompanying information) until the end of
{\bf May~4, 2020} anywhere on earth.
After this date \emph{no new entrants} will be accepted.
However, updates to existing entrants on StarExec
will be accepted until the end of {\bf May~26, 2020} anywhere on earth.

@@

\header{Dates of Competition.}
%
The bulk of the computation will take place during the weeks leading
up to SMT 2020.  Intermediate results will be regularly posted to the
SMT-COMP website as the competition runs.
%
The organizers reserve the right to prioritize certain competition
tracks or divisions to ensure their timely completion, and in
exceptional circumstances to complete divisions after the SMT
Workshop.

@@

\header{New benchmarks.}
The deadline for submission of new benchmarks is {\bf March~1, 2020}.
The organizers, in collaboration with the SMT-LIB maintainers, will be
checking and curating these until {\bf April~20, 2020}.  The SMT-LIB
maintainers intend to make a new release of the benchmark library
publicly available on or close to this date.

@@

SMT-COMP 2020 is organized under the direction of the SMT Steering
Committee. The organizing team is
%
\begin{itemize}
\setlength{\itemsep}{0pt}
\item \href{http://homepages.dcc.ufmg.br/~hbarbosa/}{Haniel Barbosa}~-- Universidade Federal de Minas Gerais, Brazil
\item \href{https://jochen-hoenicke.de/}{Jochen Hoenicke}~-- Universit\"at Freiburg, Germany
\item \href{http://www.inf.usi.ch/postdoc/hyvarinen/}{Antti Hyv\"arinen}~--
    Universit\`a della Svizzera italiana, Switzerland (chair)
\end{itemize}
%
The competition chairs are responsible for policy and procedure decisions,
such as these rules, with input from the co-organizers.

>>>>

\title{15th International Satisfiability Modulo Theories Competition
  (SMT-COMP 2021): Rules and Procedures}

@@

\begin{description}
\item[March~15] Deadline for new benchmark contributions.
\item[May~7] Final versions of competition tools (e.g., benchmark
  scrambler) are made available.  Benchmark libraries are frozen.
\item[May~30] Deadline for first versions of solvers (for all tracks),
  including information about which tracks and divisions are being
  entered, and magic numbers for benchmark scrambling.
\item[June~13] Deadline for final versions of solvers, including
  system descriptions.
\item[June~15] Opening value of NYSE Composite Index used to compute
  random seed for competition tools.
\item[July~18/19] SMT Workshop; end of competition, presentation of
  results.
\end{description}

@@

SMT-COMP~2021 is part of the SMT Workshop~2021
(\url{http://smt-workshop.cs.uiowa.edu/2021/}),
which is affiliated with CAV~2021 (\url{http://i-cav.org/2021/}).
The SMT Workshop will include a block of time to present the results of the
competition.
%
Accordingly, researchers are highly encouraged to submit both new
benchmarks and new or improved solvers to raise the level of
competition and advance the state-of-the-art in automated SMT problem
solving.

SMT-COMP 2021 will have four tracks: the \maintrack (before 2019: Main Track),
the \inctrack (before 2019: Application Track), the \ucoretrack, and the
\mvaltrack.
%
Within each track there are multiple divisions, where each division
uses benchmarks from a specific SMT-LIB logic (or group of logics).
We will recognize winners as measured by number of benchmarks solved
(taking into account the weighting detailed in
Section~\ref{sec:scoring}); we will also recognize solvers based on
additional criteria.

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Liana Hadarean,
  Matthias Heizmann, Aina Niemetz, Albert Oliveras, Giles Reger, Aaron Stump,
  and Tjark Weber.}  describes the rules and competition procedures for
SMT-COMP~2021.
%
As in previous years, we have revised the rules slightly.  Some rule
changes in 2021 are designed to not overly punish solvers producing
syntactically wrong output, by treating those outputs as unknown and
not as unsoundness.  Moreover, we added more divisions to the model
validation track.
%
The principal changes from the previous competition rules are the following:
\begin{itemize}
  \item {\bf The option \akey{:print-success} is explicitly set to
    true or false.}  Previous competitions set this option to
    \akey{true} for the incremental track.  In addition, this
    competition will set the option to \akey{false} for all other
    tracks.
    \rationale{According to the standard the default value of
      \akey{:print-success} is true.  So a conforming solver would
      unnecessarily print \akey{success} after each command that needs
      to be stored and skipped by the post-processors.  Additionally,
      solvers can use this option as indication whether incremental
      checking is desired.}

@@

SMT-COMP entrants must be submitted via StarExec (solvers) \emph{and}
the above web form (accompanying information) until the end of
{\bf May~30, 2021} anywhere on earth.
After this date \emph{no new entrants} will be accepted.
However, updates to existing entrants on StarExec
will be accepted until the end of {\bf June~13, 2021} anywhere on earth.

@@

\header{Dates of Competition.}
%
The bulk of the computation will take place during the weeks leading
up to SMT 2021.  Intermediate results will be regularly posted to the
SMT-COMP website as the competition runs.
%
The organizers reserve the right to prioritize certain competition
tracks or divisions to ensure their timely completion, and in
exceptional circumstances to complete divisions after the SMT
Workshop.

@@

\header{New benchmarks.}
The deadline for submission of new benchmarks was {\bf March~15, 2021}.
The organizers, in collaboration with the SMT-LIB maintainers, will be
checking and curating these until {\bf May~7, 2021}.  The SMT-LIB
maintainers intend to make a new release of the benchmark library
publicly available on or close to this date.

@@

SMT-COMP 2021 is organized under the direction of the SMT Steering
Committee. The organizing team is
%
\begin{itemize}
\setlength{\itemsep}{0pt}
\item \href{http://homepages.dcc.ufmg.br/~hbarbosa/}{Haniel Barbosa}~-- Universidade Federal de Minas Gerais, Brazil
\item \href{https://jochen-hoenicke.de/}{Jochen Hoenicke}~-- Universit\"at Freiburg, Germany (chair)
\item \href{http://www.inf.usi.ch/postdoc/hyvarinen/}{Antti Hyv\"arinen}~--
    Universit\`a della Svizzera italiana, Switzerland
\end{itemize}
%
The competition chairs are responsible for policy and procedure decisions,
such as these rules, with input from the co-organizers.
